Price of Anarchy for Mean Field Games

### 2018-07-23 PoA.tex
update prop 6 second half

%	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty \qquad \text{and } \qquad \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	We first provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough. Let $\epsilon_1 > 0$ satisfy $\epsilon_1 < \min \{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \}$, there exists $\bar{b}_2^{*,u} := \bar{b}^{*,u}_2(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have
	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert \right\} \leq \epsilon_1. $$ 
	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$:
	\begin{IEEEeqnarray*}{rCl}
		\vert u_t^{\bar{b}_2} \vert &=& \frac{\displaystyle C^{u,\bar{b}_2} \left(1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) }{\displaystyle B^{\bar{b}_2} D^{u,\bar{b}_2} \left( 1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + \left( - \delta_u^{-,\bar{b}_2} + \delta_u^{+,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) } \\
		&\leq & \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
		&\leq & \frac{\epsilon_1 + \epsilon_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \epsilon_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_u(\epsilon_1)
	\end{IEEEeqnarray*}
	Idem, we can also have a uniform bound for $w_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough. There exists $\bar{b}_2^{*,w} := \bar{b}_2^{*,w}(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,w}$ we have:
	\begin{equation*}
		\vert w_t^{\bar{b}_2} \vert \leq \frac{\epsilon_1 + D^w (2 c_{\delta_w^{\bar{b}_2\to \infty}} + 2 \epsilon_1)}{c_{\delta_w^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_w(\epsilon_1).		
	\end{equation*}
	Let $\bar{b}^{*,upper}_2 = \max\{ \bar{b}_2^{*,u}, \bar{b}_2^{*,w} \}$ and $M(\epsilon_1) = \max\{ M_u(\epsilon_1), M_v(\epsilon_1) \}$, then we have
	\begin{equation}
	 \sup_{\bar{b}_2 \geq \bar{b}_2^{*,1}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M(\epsilon_1).
	 \label{eq:u_t_w_t_uniform_bound_b2_bar_infty}
	\end{equation}

@@

	Now, we are ready to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC = 0$. For any given $\epsilon > 0$, 
	%we split the interval $[0,T]$ into two parts $[0,t_\epsilon]$ and $ [t_\epsilon, T]$ in which $0< t_\epsilon < T$ is a time point depending on $\epsilon$, 
	we split the interval $[0,T]$ into two parts $[0,\frac{T}{2}]$ and $ [\frac{T}{2}, T]$,
	and then we bound separately the following terms in terms of $\epsilon$:
	$$ I_1 = \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I_2 = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds. $$

@@

	Let $\epsilon_2 >0$ such that $ c_u > \epsilon_2$, there must exist $\bar{b}_2^{*,1} :=\bar{b}_2^{*,1}(\epsilon_2) > \max\{\bar{b}_2^{*,u,inc}, \bar{b}_2^{*,w,inc} \} $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,1}$ and all $s \in [0,\frac{T}{2}]$ we have:
	$$ c_u - \epsilon_2 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \epsilon_2$$
	$$ \left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \epsilon_2, \quad and \quad 
	\left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \epsilon_2.$$
	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,1}$ we have
	\begin{IEEEeqnarray}{rCl}
		I_1 &=& \frac{1}{2} B^{\bar{b}_2} \int_0^{\frac{T}{2}}  (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds  \nonumber \\
		&=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^{\frac{1}{2}} \int_0^t (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} ds} dt \nonumber \\
		&\leq& \frac{\mathbb{E}(\xi)^2 [2 \epsilon_2^2 + 2 (c_w + \epsilon_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2( r + \bar{r}(1-\bar{s})^2)} \int_0^{\frac{T}{2}} \exp \left(- \frac{2}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^{\frac{1}{2}} \cdot (c_u - \epsilon_2) t \right) dt \nonumber \\
		&=& \kappa_1(\epsilon_2) \frac{1}{(b_2 + \bar{b}_2)^{\frac{1}{2}} } \left( 1 - e^{- \kappa_2(\epsilon_2) (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right)\nonumber \\
		&\leq& \frac{\kappa_1(\epsilon_2)}{\sqrt {b_2 + \bar{b}_2} } \nonumber
	\end{IEEEeqnarray} 
	where $\displaystyle \kappa_1(\epsilon_2) = \frac{\mathbb{E}(\xi)^2 [\epsilon_2^2 + (c_w + \epsilon_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \epsilon_2)}$ and $ \displaystyle \kappa_2(\epsilon_2) = \frac{(c_u - \epsilon_2)T}{r+ \bar{r}(1-\bar{s})^2}$ are two positive constant independent of $\bar{b}_2$.
	We can then choose $\bar{b}_2^{*,I_1} := \max \{ \bar{b}_2^{*,1}(\epsilon_2), \left( \frac{\kappa_1(\epsilon_2)}{\epsilon} \right)^2 - b_2 \} $ so that for any $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$ we have 
	\begin{equation}
	I_1 \leq \frac{\kappa_1(\epsilon_2)}{\sqrt{b_2 + \bar{b}_2}} \leq \epsilon.
	\label{eq:I_1_b2_bar_infinity}
	\end{equation}

	% the term I_2
	Now, we look the term $I_2$. Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{MFG,\bar{b}_2}$ are continuous over $[\frac{T}{2},T]$, then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[\frac{T}{2},T]$ and differentiable over $(\frac{T}{2},T)$. Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $t_1$ and $t_2$ depending on $\bar{b}_2$ which satisfy $\frac{T}{2} < t_1 < T$ and $0 < t_2 < t_1 <T$ such that:
	\begin{IEEEeqnarray}{rCl}
		I_2 &=& \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_t- w^{\bar{b}_2}_t)^2 (\bar{x}_t^{MFG, \bar{b}_2} )^2 dt  \nonumber \\
		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{MFG,\bar{b}_2} )^2  \cdot \frac{T}{2} \nonumber \\
		&=& \frac{T  B^{\bar{b}_2} }{4} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds \right) \nonumber \\
		&\leq &  \kappa_3 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot (b_2 + \bar{b}_2)^2 \exp\left( - 2 B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1 \right) \nonumber \\
		&\leq & \kappa_3 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot (b_2 + \bar{b}_2)^2 \exp \left( - \kappa_4 (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2,t_2) \right),
		\label{eq:I_2_b2_bar_inequality}
	\end{IEEEeqnarray}
	where   $\displaystyle \kappa_3 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) T}}{4 (r + \bar{r}(1-\bar{s})^2)}$ and $\displaystyle \kappa_4 = \frac{T}{(r + \bar{r}(1-\bar{s})^2)} $ are two positive constants independent of $\bar{b}_2$, and $ \displaystyle h(\bar{b}_2,t) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t}^{\bar{b}_2}$.

	We are going to bound that the last term in (\ref{eq:I_2_b2_bar_inequality}). To do so, we recall that from equation (\ref{eq:u_t_lower_bound_b2_bar_infty}), we have for all $t \in [0,T]$ and all $\bar{b}_2 \geq \bar{b}_2^{*,lower}$ the inequality $ \inf_{0 \leq s \leq T} h(\bar{b}_2,s) \geq m_u(\epsilon_1)$. 
	Let $\epsilon_3>0$ such that $m_u(\epsilon_1) -  \epsilon_3 >0$. Then there exists $\bar{b}_2^{*,2} = \bar{b}_2^{*,2}(\epsilon_1,\epsilon_3)$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,2}$ we have: 
	$$ 2 \ln(b_2 + \bar{b}_2) - \epsilon_3\kappa_4 \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \leq 0.$$ 
	Hence, let $\bar{b}_2^{*,3} = \max \{\bar{b}_2^{*,upper}, \bar{b}_2^{*,2}, \bar{b}_2^{*,lower} \}$ and together with inequality (\ref{eq:u_t_w_t_uniform_bound_b2_bar_infty}) and (\ref{eq:I_2_b2_bar_inequality}), we obtain that for all $\bar{b}_2 \geq \bar{b}_2^{*,3}$:
	\begin{IEEEeqnarray*}{rCl}
		I_2 &\leq& \kappa_3 \cdot 4 M(\epsilon_1)^2 \cdot (b_2 + \bar{b}_2)^2 \exp \left( - \kappa_4 (b_2 + \bar{b}_2)^{\frac{1}{2}} m_u(\epsilon_1) \right) \nonumber \\
		&=& 4\kappa_3 M(\epsilon_1)^2 e^{ 2 \ln(b_2 + \bar{b}_2) - \epsilon_3 \kappa_4 \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}}} \cdot \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right)   \nonumber \\
		&\leq & \kappa_5(\epsilon_1) \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right)
	\end{IEEEeqnarray*}
	where $\kappa_5 = 4 \kappa_3 M(\epsilon_1)^2$ is independent of $\bar{b}_2$. Now, we set $\bar{b}^{*,I_2}_2 := \max\{ \bar{b}_2^{*,3},  \left( \frac{ \ln( \kappa_5(\epsilon_1) / \epsilon)}{ \kappa_4 (m_u(\epsilon_1) - \epsilon_3)} \right)^2 - b_2 \}$, then we have for all $\bar{b}_2 \geq \bar{b}_2^{*,I_2}$,
	\begin{equation}
		I_2 \leq \kappa_5(\epsilon_1) \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right) \leq \epsilon.
	\label{eq:I_2_b2_bar_infinity}
	\end{equation}

	Hence, from inequality (\ref{eq:I_1_b2_bar_infinity}) and (\ref{eq:I_2_b2_bar_infinity}), for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
	\begin{equation*}
		\Delta SC = I_1 + I_2 \leq 2\epsilon.
	\end{equation*} 
	Therefore, by taking $\epsilon \to 0$, we obtain:
	\begin{equation*}
		\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.
	\end{equation*}

>>>>

%	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty \qquad \text{and } \qquad \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	We first provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough. Let $\epsilon_1 > 0$ satisfy $\epsilon_1 < \min \{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \}$, there exists $\bar{b}_2^{*,u} := \bar{b}^{*,u}_2(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have
	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert \right\} \leq \epsilon_1. $$ 
	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$:
	\begin{IEEEeqnarray*}{rCl}
		\vert u_t^{\bar{b}_2} \vert &=& \frac{\displaystyle C^{u,\bar{b}_2} \left(1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) }{\displaystyle B^{\bar{b}_2} D^{u,\bar{b}_2} \left( 1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + \left( - \delta_u^{-,\bar{b}_2} + \delta_u^{+,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) } \\
		&\leq & \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
		&\leq & \frac{\epsilon_1 + \epsilon_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \epsilon_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_u(\epsilon_1)
	\end{IEEEeqnarray*}
	Idem, we can also have a uniform bound for $w_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough. There exists $\bar{b}_2^{*,w} := \bar{b}_2^{*,w}(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,w}$ we have:
	\begin{equation*}
		\vert w_t^{\bar{b}_2} \vert \leq \frac{\epsilon_1 + D^w (2 c_{\delta_w^{\bar{b}_2\to \infty}} + 2 \epsilon_1)}{c_{\delta_w^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_w(\epsilon_1).		
	\end{equation*}
	Let $\bar{b}^{*,upper}_2 = \max\{ \bar{b}_2^{*,u}, \bar{b}_2^{*,w} \}$ and $M(\epsilon_1) = \max\{ M_u(\epsilon_1), M_v(\epsilon_1) \}$, then we have
	\begin{equation}
	 \sup_{\bar{b}_2 \geq \bar{b}_2^{*,upper}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M(\epsilon_1).
	 \label{eq:u_t_w_t_uniform_bound_b2_bar_infty}
	\end{equation}

@@

	Now, we are ready to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC = 0$. For any given $\epsilon > 0$, 
	%we split the interval $[0,T]$ into two parts $[0,t_\epsilon]$ and $ [t_\epsilon, T]$ in which $0< t_\epsilon < T$ is a time point depending on $\epsilon$, 
	we split the interval $[0,T]$ into two parts $[0,\frac{T}{2}]$ and $ [\frac{T}{2}, T]$,
	and then we bound separately the following two quantities in terms of $\epsilon$:
	$$ I_1 = \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I_2 = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds. $$

@@

	Let $\epsilon_2 >0$ such that $ c_u > \epsilon_2$, there must exist $\bar{b}_2^{*,1} :=\bar{b}_2^{*,1}(\epsilon_2) > \max\{\bar{b}_2^{*,u,inc}, \bar{b}_2^{*,w,inc} \} $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,1}$ and all $s \in [0,\frac{T}{2}]$ we have:
	$$ c_u - \epsilon_2 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \epsilon_2$$
	$$ \left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \epsilon_2, \quad and \quad 
	\left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \epsilon_2.$$
	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,1}$ we have
	\begin{IEEEeqnarray}{rCl}
		I_1 &=& \frac{1}{2} B^{\bar{b}_2} \int_0^{\frac{T}{2}}  (u^{\bar{b}_2}_t- w^{\bar{b}_2}_t)^2 (\bar{x}_t^{MFG, \bar{b}_2} )^2 dt  \nonumber \\
		&=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^{\frac{1}{2}} \int_0^t (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} ds} dt \nonumber \\
		&\leq& \frac{\mathbb{E}(\xi)^2 [2 \epsilon_2^2 + 2 (c_w + \epsilon_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2( r + \bar{r}(1-\bar{s})^2)} \int_0^{\frac{T}{2}} \exp \left(- \frac{2}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^{\frac{1}{2}} \cdot (c_u - \epsilon_2) t \right) dt \nonumber \\
		&=& \kappa_1(\epsilon_2) \frac{1}{(b_2 + \bar{b}_2)^{\frac{1}{2}} } \left( 1 - e^{- \kappa_2(\epsilon_2) (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right)\nonumber \\
		&\leq& \frac{\kappa_1(\epsilon_2)}{\sqrt {b_2 + \bar{b}_2} } \nonumber
	\end{IEEEeqnarray} 
	where $\displaystyle \kappa_1(\epsilon_2) = \frac{\mathbb{E}(\xi)^2 [\epsilon_2^2 + (c_w + \epsilon_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \epsilon_2)}$ and $ \displaystyle \kappa_2(\epsilon_2) = \frac{(c_u - \epsilon_2)T}{r+ \bar{r}(1-\bar{s})^2}$ are two positive constant independent of $\bar{b}_2$.
	We can then choose $\bar{b}_2^{*,I_1} := \max \{ \bar{b}_2^{*,1}(\epsilon_2), \left( \frac{\kappa_1(\epsilon_2)}{\epsilon} \right)^2 - b_2 \} $ so that for any $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$ we have 
	\begin{equation}
	I_1 \leq \frac{\kappa_1(\epsilon_2)}{\sqrt{b_2 + \bar{b}_2}} \leq \epsilon.
	\label{eq:I_1_b2_bar_infinity}
	\end{equation}

	% the term I_2
	Now, we look the term $I_2$. Since $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[T/2,T]$, then the functions $\displaystyle t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[T/2,T]$ and differentiable over $(T/2,T)$. Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed time points $t_1$ and $t_2$ depending on $\bar{b}_2$ which satisfy $\frac{T}{2} < t_1 < T$ and $0 < t_2 < t_1 <T$ such that:
	\begin{IEEEeqnarray}{rCl}
		I_2 &=& \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_t- w^{\bar{b}_2}_t)^2 (\bar{x}_t^{MFG, \bar{b}_2} )^2 dt  \nonumber \\
		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{MFG,\bar{b}_2} )^2  \cdot \frac{T}{2} \nonumber \\
		&=& \frac{T  B^{\bar{b}_2} }{4} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds \right) \nonumber \\
		&\leq &  \kappa_3 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot (b_2 + \bar{b}_2)^2 \exp\left( - 2 B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1 \right) \nonumber \\
		&\leq & \kappa_3 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot (b_2 + \bar{b}_2)^2 \exp \left( - \kappa_4 (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2,t_2) \right),
		\label{eq:I_2_b2_bar_inequality}
	\end{IEEEeqnarray}
	where   $\displaystyle \kappa_3 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) T}}{4 (r + \bar{r}(1-\bar{s})^2)}$ and $\displaystyle \kappa_4 = \frac{T}{(r + \bar{r}(1-\bar{s})^2)} $ are two positive constants independent of $\bar{b}_2$, and $ \displaystyle h(\bar{b}_2,t) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t}^{\bar{b}_2}$.

	We are going to bound that the last term in (\ref{eq:I_2_b2_bar_inequality}). To do so, we recall that from equation (\ref{eq:u_t_lower_bound_b2_bar_infty}), we have for all $t \in [0,T]$ and all $\bar{b}_2 \geq \bar{b}_2^{*,lower}$ the inequality $ \inf_{0 \leq s \leq T} h(\bar{b}_2,s) \geq m_u(\epsilon_1)$. 
	Let $\epsilon_3>0$ such that $m_u(\epsilon_1) -  \epsilon_3 >0$. Then there exists $\bar{b}_2^{*,2} = \bar{b}_2^{*,2}(\epsilon_1,\epsilon_3)$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,2}$ we have: 
	$$ 2 \ln(b_2 + \bar{b}_2) - \epsilon_3\kappa_4 \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \leq 0.$$ 
	Hence, let $\bar{b}_2^{*,3} = \max \{\bar{b}_2^{*,upper}, \bar{b}_2^{*,lower}, \bar{b}_2^{*,2} \}$ and together with inequality (\ref{eq:u_t_w_t_uniform_bound_b2_bar_infty}) and (\ref{eq:I_2_b2_bar_inequality}), we obtain that for all $\bar{b}_2 \geq \bar{b}_2^{*,3}$:
	\begin{IEEEeqnarray*}{rCl}
		I_2 &\leq& \kappa_3 \cdot 4 M(\epsilon_1)^2 \cdot (b_2 + \bar{b}_2)^2 \exp \left( - \kappa_4 (b_2 + \bar{b}_2)^{\frac{1}{2}} m_u(\epsilon_1) \right) \nonumber \\
		&=& 4\kappa_3 M(\epsilon_1)^2 e^{ 2 \ln(b_2 + \bar{b}_2) - \epsilon_3 \kappa_4 \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}}} \cdot \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right)   \nonumber \\
		&\leq & \kappa_5(\epsilon_1) \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right)
	\end{IEEEeqnarray*}
	where $\kappa_5 = 4 \kappa_3 M(\epsilon_1)^2$ is independent of $\bar{b}_2$. Now, we set $\bar{b}^{*,I_2}_2 := \max\{ \bar{b}_2^{*,3},  \left( \frac{ \ln( \kappa_5(\epsilon_1) / \epsilon)}{ \kappa_4 (m_u(\epsilon_1) - \epsilon_3)} \right)^2 - b_2 \}$, then we have for all $\bar{b}_2 \geq \bar{b}_2^{*,I_2}$,
	\begin{equation}
		I_2 \leq \kappa_5(\epsilon_1) \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right) \leq \epsilon.
	\label{eq:I_2_b2_bar_infinity}
	\end{equation}

	Hence, from inequalities (\ref{eq:I_1_b2_bar_infinity}) and (\ref{eq:I_2_b2_bar_infinity}), for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
	\begin{equation*}
		\Delta SC = I_1 + I_2 \leq 2\epsilon.
	\end{equation*} 
	Therefore, by taking $\epsilon \to 0$, we obtain:
	\begin{equation*}
		\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.
	\end{equation*}
